A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-10-15 doc/types-pldi2013/evaluation.tex

We evaluate the Legion type system on three criteria:
\begin{itemize}
\item Expressivity: Can real applications be written (Section~\ref{subsec:expressivity})?
\item Overhead: Does it reduce checking costs (Section~\ref{subsec:overhead})?
\item Scalability: Can it leverage hierarchical scheduling (Section~\ref{subsec:scalability})?
\end{itemize}
%Our evaluation uses a prototype implementation of the Legion language and programming model.
Our prototype implementation has two components: a type checker
for the language introduced in Section~\ref{sec:legioncore} and a C++ runtime library
for executing programs written in the Legion programming model\cite{Legion12}.  All experiments
are conducted on the Keeneland supercomputer\cite{Keeneland}.  Each node of the Keeneland
machine consists of two Xeon 5660 CPUs, three Tesla M2090 GPUs, and 24 GB of DRAM.  Nodes
are connected by a QDR Infiniband interconnect.

@@

>>>>

We evaluate the Legion type system on four criteria:
\begin{itemize}
\item Expressivity: Can real applications be written (Section~\ref{subsec:expressivity})?
\item Overhead: Does it reduce checking costs (Section~\ref{subsec:overhead})?
\item Scalability: Can it leverage hierarchical scheduling (Section~\ref{subsec:scalability})?
\item Performance: Does the performance increase from relaxed coherence modes (Section~\ref{subsec:relaxedperf})
warrant the increased complexity in the operational semantics?
\end{itemize}
%Our evaluation uses a prototype implementation of the Legion language and programming model.
Our prototype implementation has two components: a type checker
for the language introduced in Section~\ref{sec:legioncore} and a C++ runtime library
for executing programs written in the Legion programming model\cite{Legion12}.  All experiments
are conducted on the Keeneland supercomputer\cite{Keeneland}.  Each node of the Keeneland
machine consists of two Xeon 5660 CPUs, three Tesla M2090 GPUs, and 24 GB of DRAM.  Nodes
are connected by a QDR Infiniband interconnect.

@@

\subsection{Performance}
\label{subsec:relaxedperf}

To demonstrate the benefit of relaxed coherence modes, we modified the circuit example from Section~\ref{sec:example}
to use exclusive coherence in the {\em distribute\_charge} task and compared the performance of the two versions.
The results are shown in Figure~\ref{fig:circuit_excl}.  Even though the {\em distribute\_charge} tasks
are a small fraction of the total work, the serialization that results from requiring exclusive access to the 
overlapping ghost regions limits the scalability of the application, as would be expected from Amdahl's Law.
